ICT-Specific Investment Shocks and Economic Fluctuations

### 2019-03-06 Latex/Conference_Modena_March2019/Brianti Gati March 2019.tex
more on presentation

\documentclass[hyperref={pdfpagelabels=false}]{beamer}
\setbeamercolor{background canvas}{bg=white}
\usepackage{graphicx,lmodern,subfigure,ulem,color,graphicx,tikz,booktabs,natbib}
\usepackage{subfig}
\usepackage{mathrsfs}
\usepackage{subfigure}
\usetheme{Warsaw}
%\definecolor{beamer@blendedblue}{rgb}{0.1,0.5,0.1}
%\definecolor{ForestGreen}{RGB}{60, 140, 60}
%\setbeamercolor{structure}{fg=beamer@blendedblue}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[frame number]
\bibliographystyle{chicago}
\newcommand{\spitem}{\vspace{.3cm}\item}
\newcommand{\elas}{$E_{labor}$}
%\def \FigPath {Users\th3\Documents\Job_Market_Paper\Code\Figures} 
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage{makecell}

@@

In this paper we focus on the \textbf{slowdown in TFP},
\begin{itemize}
	\item[$\Rightarrow$] Which variable actually boost productivity? Why? 
	\item[$\Rightarrow$] Can this variable explain the recent slowdown in TFP?
\end{itemize}

@@

	We follow an alternative avenue and focus on the relation between \textbf{Information and Communication Technology Investment} (ICTI) and total factor productivity
	\begin{itemize}
			\item \textit{Expenditure in equipment and computer software meant to be used in production (as an input) for more than a year.}
			\end{itemize}

@@

	\begin{enumerate}
		\item \textbf{Empirical evidence} that contemporaneous jumps in ICTI explain significant and persistent increases in future TFP
		\begin{itemize}
			\item SVAR techniques on U.S. aggregates to identify supply shocks specific to the ICT sector
		\end{itemize}

@@

	We estimate a structural VAR using aggregate, quarterly US data from 1989Q1 to 2017Q2.

@@

\begin{figure}
	\centering
	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}}\qquad
	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}}\qquad
	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}}\qquad

		\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}}\qquad
	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}}\qquad
	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}}\qquad
\end{figure}

@@

\frame{\frametitle{Robustness Checks and Related Exercises}

	\begin{itemize}
		\item ICT shocks are \textbf{important driver} of business cycle fluctuations
	\begin{itemize}
		\item[-] Almost $100$\% of ICT investment on impact
		\item[-] Around $30$\% of TFP fluctuations over 10-year horizon 
		\item[-] Almost $40$\% of GDP fluctuations over BC frequencies
	\end{itemize}

@@

\item \textbf{Results are robust} to
\begin{itemize}
	\item[-] Changing the available information in the system
	\begin{itemize}
	\item[$\rightarrow$] Estimated ICT shocks pass Forni-Gambetti test
	\end{itemize}
	\item[-] Not controlling for contemporaneous TFP
	\item[-] Controlling for news shocks \`a la Barsky and Sims
	\item[-] Controlling for other shocks
	\begin{itemize}
		\item[$\rightarrow$] Ramey Military News 
		\item[$\rightarrow$]  Romer-Romer Monetary Policy 
		\item[$\rightarrow$]  \dots
	\end{itemize}
\end{itemize}
\end{itemize}

>>>>

\documentclass[hyperref={pdfpagelabels=false}]{beamer}
\setbeamercolor{background canvas}{bg=white}
\usepackage{graphicx,lmodern,subfigure,ulem,color,graphicx,tikz,booktabs,natbib}
%\usepackage{subfig}
\usepackage{mathrsfs}
\usepackage{subfigure}
\usetheme{Warsaw}
%\definecolor{beamer@blendedblue}{rgb}{0.1,0.5,0.1}
%\definecolor{ForestGreen}{RGB}{60, 140, 60}
%\setbeamercolor{structure}{fg=beamer@blendedblue}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[frame number]
\bibliographystyle{chicago}
\newcommand{\spitem}{\vspace{.3cm}\item}
\newcommand{\elas}{$E_{labor}$}
%\def \FigPath {Users\th3\Documents\Job_Market_Paper\Code\Figures} 
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage{makecell}

@@

In this paper we focus on the \textbf{slowdown in TFP},
\begin{itemize}
	\item[$\Rightarrow$] Which variable actually boosted productivity in the last three decades? Why? 
\end{itemize}

@@

	We follow an alternative avenue and focus on the relation between \textbf{Information and Communication Technology Investment} (ICTI) and total factor productivity
	\begin{itemize}
			\item \textit{Acquisition of equipment and computer software meant to be used in production for more than a year.}
			\end{itemize}

@@

	\begin{enumerate}
		\item \textbf{Empirical Contribution} that contemporaneous jumps in ICTI explain significant and persistent increases in future TFP
		\begin{itemize}
			\item Structural VAR techniques on U.S. aggregates to identify ICT investment shocks
		\end{itemize}

@@

	We estimate a structural VAR using aggregate quarterly US data from 1989Q1 to 2017Q2.

@@

%\begin{figure}
%	\centering
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}}\qquad
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}}\qquad
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}}\qquad

%		\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}}\qquad
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}}\qquad
%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}}\qquad
%\end{figure}

@@

\frame{\frametitle{Variance Decomposition Analysis and Robustness Checks}

	\begin{itemize}
		\item ICT shocks are an \textbf{important driver} of economic fluctuations
	\begin{itemize}
		\item[-] Around $30$\% of TFP fluctuations over 10-year horizon 
		\item[-] Almost $40$\% of GDP fluctuations over BC frequencies
	\end{itemize}

@@

\item \textbf{Results are robust} after
\begin{itemize}
	\item[-] controlling for news shocks \`a la Barsky and Sims
	\item[-] controlling for other shocks estimated via narrative approach
     \item[-] ordering TFP after ICT investment
\end{itemize}

\end{itemize}
